\SW Collaboration Publication Policy: CFHT-LS

### 2014-05-16 doc/sw-publication-policy-cfhtls.tex
Minor clean-up after merge from AV
Hangout with A&A to sort out author list
Updates to policies, author_core.tex, renew command for \comment

\item{\bf Principal Investigators:} These are the PIs of the \sw project (P.\,Marshall, 
A.\,More and A.\,Verma)\footnote{The PIs may be collectively contacted via the email address spacewarpspi@googlegroups.com}

@@

\item{\bf Community} All of the volunteers who have contributed
classifications to the project\footnote{We can only communicate directly with those who have logged in with a Zooniverse ID via \Talk or group e-mail.}.

@@

%First, however, we remind ourselves about data access via \sw.

%\section{Survey Data Use}
%\label{sec:data}

%\sw is a public website. All images displayed there are by definition in the
%public domain, and so must be expected to be downloaded, copied and
%redistributed by any \sw user. This is a \textbf{good thing}: images of the sky taken
%with publicly-funded telescopes belong to everyone. It is the responsibility
%of the survey science teams to provide images in a way that is consistent
%with their own data access rules.

%While the CFHT-LS is a public survey, the WCS information has been removed from the provided images. This prevents the follow-up of any of the objects in the survey by anyone other than the \sw
%team. In practice, the objects contained in the \sw images will be too faint
%for anyone without access to a large telescope to observe, and may also be
%absent from any public catalogs, so the opportunities for follow-up will be
%quite limited. Removing the WCS information is an insurance policy against any
%competing professional scientists looking to ``scoop'' the survey team,
%despite the damage it would do to their reputations.\footnote{We cannot exclude the possibility that object co-ordinates are posted in \Talk. For example, co-ordinates of previously published lens candidates or recognisable fields from CFHT-LS have appeared in \Talk.}

@@

\begin{itemize}
% Old versions of this list, which caused a conflict when I (PJM) merged in
% Aprajita's May 2014 edits. Both look out of date to me! Suggested new 
% version is beneath these.
% 
% <<<<<<< HEAD
% \item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
% \item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates. 
% \item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
% \item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
% \item \sw X: New lenses(s) in \sw (authored by collaboration members)
%
% =======
% \item \sw I: The system paper, describing the project, the interface, the
% classification analysis methods (SWAP) and results 
% \item \sw II: The \sw  simulations and community performance (not selection
% function), means by which you can compute a selection function for any given
% analysis. 
% \item \sw III: The first new candidates from CFHT-LS \textit{including models,
% follow-up if feasible}
% \item \sw IV: The results from CFHT-LS search including the comparison and
% analysis of citizen scientist classification versus lens-finding algorithms
% (maybe split into smaller papers).
% >>>>>>> 34d2fe73486cc68b301665b1b811cff7804137e8
%
\item \sw I: The system paper, describing the project, the interface \& training scheme, the classification analysis methods (SWAP) and results from classification of the training set. (Marshall et al.)
\item \sw II: The \sw CFHTLS project, including description of CFHT-LS specific information (e.g. data/subjects, generation of simulated images), results new lens candidates, and preliminary analysis of \sw compared to previous semi-automatic lens searches in this survey. (More et al.)
\item \sw III: Detailed comparison and analysis of citizen scientist classification versus lens-finding. (More et al.)
%AV to PJM: i thought Anu still wanted the sim-automated serach comparison to be considered in a separate paper
\item \sw IV-X: Detailed results on candidates from CFHT-LS \textit{including lens models, follow-up etc.} (IV: Verma et al. \& authored by collaboration members)
\end{itemize}

@@

\subsection{\sw Related Papers}
These are \sw related papers but do not necessarily fall into the \sw paper series. Planned examples are:
\begin{itemize}
\item Lens modelling in \sw with {\sc Spaghetti Lens})
\item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
\end{itemize}

% PJM: not sure if this section should be here, it was part of a conflict I 
% got when I merged... Aprajita?
% AV: It was supposed to be here, is a procedure for collaborators to suggest papers

@@

The current list of \sw authors is given in the \texttt{authors.tex} file and is reprinted
in the appendix to this document (see Appendix \ref{sec:appa}); this file shown is as it is currently configured, ready to be copied and pasted into the \sw system paper (\sw I).

\noindent The author categories are grouped according to collaboration membership (defined above). These authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names based on what they have contributed.

For the CFHT-LS \sw system papers, the Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.

@@

Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments. If  ``opt-in'' authors have not provided comments within this time frame they will *not* be included as authors on the paper. If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.

For \sw related papers, the \sw PIs should be contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} for a suggested minimum contingent of collaboration authors to be added to the paper, consistent with the policy for general/future \sw projects (please see Guidelines and Policy for Surveys using \sw in this directory).

@@

Any \sw collaboration member, simply by virtue of their Zooniverse
registration, may write a Zooniverse
Letter\footnote{\texttt{http://letters.zooniverse.org}} describing their
investigation of any lens candidate they find in \sw. This, along with
posts in  \Talk, are the primary means by which we expect collaboration
members will communicate their findings to the rest of the
astronomical community. 
The \sw Zooniverse \Letters will contribute to the collective knowledge and understanding of the presented system(s). 
Zooniverse \Letters are citable
objects, and in some cases will appear listed on ADS.\footnote(To be confirmed.)
We strongly encourage community members to write Zooniverse \Letters about their findings. We would be happy to help any member wishing to do this, please just drop us a line at spacewarpspi@googlegroups.com.

@@

\appendix
\section{Current Author List for \sw series papers:}
\label{sec:appa}
{\small \verbatiminput{authors.tex}}

>>>>

\item{\bf Principal Investigators:} These are the PIs of the \sw project (P.\,Marshall, 
A.\,More and A.\,Verma)\footnote{The PIs may be collectively contacted via the email address \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}}

@@

\item{\bf Community:} All of the volunteers who have contributed
classifications to the project\footnote{We can only communicate directly with those who have logged in with a Zooniverse ID via \Talk or group e-mail.}.

@@

@@

\begin{itemize}

\item \sw I: The system paper, describing the project, the interface \& training scheme, the classification analysis methods (SWAP) and results from classification of the training set. (Marshall et al.)
\item \sw II: First results from the \sw CFHTLS project, including description of CFHT-LS specific information (e.g. data/subjects, generation of simulated images), new lens candidates, and preliminary analysis of \sw compared to previous semi-automatic lens searches in this survey. (More et al.)
\item \sw III: Detailed comparison and analysis of citizen scientist classification versus lens-finding algorithms. (More et al.)
\item \sw IV: Detailed analysis of candidates from CFHT-LS \textit{including lens models, follow-up etc.} (Verma et al.)
\item \sw X: Detailed results on lens systems from CFHT-LS (authored by \sw collaboration members)
\end{itemize}

@@

\subsection{\sw Related Papers}
These are \sw related papers but do not necessarily fall into the \sw paper series. Planned examples are:
\begin{itemize}
\item Lens modelling in \sw with {\sc Spaghetti Lens}
\item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
\end{itemize}

@@

The current list of \sw authors is given in the \texttt{authors\_core.tex} file and is reprinted
in the appendix to this document (see Appendix \ref{sec:appa}); this file shown is as it is currently configured, ready to be copied and pasted into the \sw system paper (\sw I).

\noindent The author categories are grouped according to collaboration membership (defined above). Authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names based on what they have contributed.

For the CFHT-LS \sw system papers, the core team have ``opt-out'' status, the remainder  and the \sw Affiliates have ``opt-in'' status.

@@

Lead authors of \sw papers should circulate drafts to the list of authors (and whoever they wish from the affiliates list) and allow a minimum of two weeks to give time for comments. If  ``opt-in'' authors have not provided comments within this time frame they will *not* be included as authors on the paper. If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.

For \sw related papers, the \sw PIs should be contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} for a suggested minimum contingent of collaboration authors to be added to the paper, but the ``opt-out'' authors defined in \texttt{authors\_core.tex} should be included as a minimum.

@@

Any \sw collaboration member, simply by virtue of their Zooniverse
registration, may write a Zooniverse
Letter\footnote{\texttt{http://letters.zooniverse.org}} describing their
investigation of any lens candidate they find in \sw. This, along with
posts in  \Talk, are the primary means by which we expect collaboration
members will communicate their findings to the rest of the
astronomical community. 
The \sw Zooniverse \Letters will contribute to the collective knowledge and understanding of the presented system(s). 
Zooniverse \Letters are citable
objects, and in some cases will appear listed on ADS.\footnote{To be confirmed.}
We strongly encourage community members to write Zooniverse \Letters about their findings. We would be happy to help any member wishing to do this, please just drop us a line at spacewarpspi@googlegroups.com.

@@

\appendix
\section{Current Author List for \sw series papers:}
\label{sec:appa}
{\small \verbatiminput{authors_core.tex}}
